D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-01 ootavacuous.tex
Clarify that OOTA cycles imply non-OOTA bugs
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

We are grateful to David Goldblatt for his careful review of an early
draft of this paper and to John Wikerson for asking Paul for a rant and
taking the proffered rant seriously.
We also owe David Goldblatt a debt of gratitude for his having asked
an insightful question at the right time.
Nonetheless, all errors and omissions in this paper are the sole property
of the authors.

% To do:
% Luc Maranget: Memory models.
% Richard Gristenthwaite: ARM hardware.
% Mark Rutland: ARM memory ordering.
% Will Deacon: ARM hardware, C++, and OOTA.
% Greg Kroah-Hartman and Linus Torvalds: FYI, trouble being caused.
% Christoph Hellwig: Why slow on BPF memory model.
% Miguel Ojeda: LKMM and Rust.
% Alice Ryhl: LKMM and Rust.
% Ralf Jung: Rust.
% Catalin Marinas: ARM and formal methods (qspinlock).
% Segher Boessenkool:  GCC.
% Dan Lustig: NVIDIA memory ordering.
% Andrea Parri: Memory models, RISC-V hardware.
% Jonas Oberhauser: Memory models.
% Hernan Ponce de Leon: Memory models.
% Palmer Dabbelt: RISC-V hardware.
% Ali Sezgin: P0422R0.
% Tony Tye: P0422R0.
% Other memory-model maintainers, including Peter Zijlstra.
% Derek Williams: PowerPC hardware.
% Hans Boehm: Skeptic, memory models, OOTA.  Suggestions for others?
% Olivier Giroux: Skeptic, memory models, NVIDIA.
% Luke Geeson: Whatever...  Review.
% Ori Lahav: Prior OOTA.
% Viktor Vafeiadis:  Prior OOTA.
% Brian Demsky: Prior OOTA.

@@

% Done:
% David Goldblatt
% Michael Wong
% Maged Michael
% John Wickerson: Thank you.  Peter Sewell?  Mark Batty? Other TFWM authors?
% Akira Yokosawa: Professional courtesy, perfbook memory models.
% Dan Kelley, Alexei Starovoitov, Mykola Lysenko: FYI.  OOTA dropped
% Alan Jeffrey: Fixed-point insight P0422R0.  Reached out via LinkedIn.
% Jade Alglave: C++ herd model?  Memory models and variety of hardware.
% Alan Stern: Memory models, mathematical logic, and variety of hardware.

>>>>

Therefore, if your C++ implementation produces OOTA cycles, you have
bugs that would be considered bugs even if OOTA cycles were allowed.
And you need to fix those bugs, regardless of whether they are in your
compiler, your hardware, or your alternative universe.

@@

We are grateful to David Goldblatt and Jade Alglave for their careful
review of an early draft of this paper and to John Wikerson for asking
Paul for a rant and taking the proffered rant seriously.
We also owe David Goldblatt a debt of gratitude for his having asked an
insightful question at the right time, and for his ``Deathstation 9000''
demonic CPU.
Nonetheless, all errors and omissions in this paper are the sole property
of the authors.

% To do:
% Luc Maranget: Memory models.
% Richard Gristenthwaite: ARM hardware.
% Mark Rutland: ARM memory ordering.
% Will Deacon: ARM hardware, C++, and OOTA.
% Greg Kroah-Hartman and Linus Torvalds: FYI, trouble being caused.
% Christoph Hellwig: Why slow on BPF memory model.
% Miguel Ojeda: LKMM and Rust.
% Alice Ryhl: LKMM and Rust.
% Ralf Jung: Rust.
% Catalin Marinas: ARM and formal methods (qspinlock).
% Segher Boessenkool:  GCC.
% Dan Lustig: NVIDIA memory ordering.
% Andrea Parri: Memory models, RISC-V hardware.
% Jonas Oberhauser: Memory models.
% Hernan Ponce de Leon: Memory models.
% Palmer Dabbelt: RISC-V hardware.
% Ali Sezgin: P0422R0.
% Tony Tye: P0422R0.
% Other memory-model maintainers, including Peter Zijlstra.
% Derek Williams: PowerPC hardware.
% Hans Boehm: Skeptic, memory models, OOTA.  Suggestions for others?
% Olivier Giroux: Skeptic, memory models, NVIDIA.
% Luke Geeson: Whatever...  Review.
% Ori Lahav: Prior OOTA.
% Viktor Vafeiadis:  Prior OOTA.
% Derek Dreyer: Prior OOTA.
% Brian Demsky: Prior OOTA.

@@

% Done:
% David Goldblatt
% Boqun Feng?
% Michael Wong
% Maged Michael
% John Wickerson: Thank you.  Peter Sewell?  Mark Batty? Other TFWM authors?
% Akira Yokosawa: Professional courtesy, perfbook memory models.
% Dan Kelley, Alexei Starovoitov, Mykola Lysenko: FYI.  OOTA dropped
% Alan Jeffrey: Fixed-point insight P0422R0.  Reached out via LinkedIn.
% Jade Alglave: C++ herd model?  Memory models and variety of hardware.
% Alan Stern: Memory models, mathematical logic, and variety of hardware.
